### 2021-07-14 src/paper/model/estimated_parameters.tex
Estimated parameter table in landscape format.
Finish going over appendix B. More type corrections, suggestions and comments.

We estimate parameters that cannot be calibrated outside of the model with the
method of simulated moments \citep{McFadden1989} by minimizing the distance between
simulated and observed infection rates and fatality rates (disaggregated by region
and age groups). Since our model includes a lot of randomness, we
average simulated infection rates over several model runs.

@@

@@

@@

% infection probabilities
To avoid over-fitting and simplify the numerical optimization problem, we only allow for
five different infection probabilities: 1) for contacts in schools 2) contacts in
preschools and nurseries. 3) for work contacts. 4) for households. 5) for other
contacts.

@@

In order to get a feeling for the infectiousness of each contact type it
is more intuitive to look at how many infections were actually caused by each contact
type. This is depicted in Figure~\ref{fig:infection_heatmap}. We can see that work and
other contacts are the main driver of the pandemic, followed by infections in
households. Schools and preschools contribute fewer infections which is to be expected
given that there are much fewer students than working adults in the German population.
Nevertheless, Figure~\ref{fig:school_scenarios_detailed} shows that schools do have a
notable effect on the infection dynamic in the long run.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/infection_channels.png}
    \caption{Daily share of infections by contact type}
    \floatfoot{\noindent \textit{Note:} Daily hare of infections that were contributed
    by each contact type. Darker colors mean that a larger share of infections were
    contributed by that contact type. The majority of infections take place in the
    workplace, in households and via other contacts. Schools and preschools contribute
    less infections, especially after hygiene measures have been introduced.}
    \label{fig:infection_heatmap}
\end{figure}

@@

Moreover, we estimate nine different multipliers that reflect how strongly other
contacts are reduced over time. The dates at which we switch between the multipliers
usually coincides with policy changes and is not determined from the data. The only
exception to this are slight adjustments to parameters to incorporate lockdown fatigue
(towards the end of a lockdown period) or precautionary contact reductions (in times
of high incidences right before a lockdown is enacted). The estimated other multipliers
are also depicted in Figure~\ref{fig:other_multiplier}.

>>>>

We estimate parameters that cannot be calibrated outside of the model with the method of
simulated moments \citep{McFadden1989} by minimizing the distance between simulated and
observed infection rates (disaggregated by region and age groups) and fatality rates.
Since our model includes a lot of randomness, we average simulated infection rates over
several model runs.

@@

\begin{landscape}

@@

\end{landscape}

@@

% infection probabilities
To avoid over-fitting and simplify the numerical optimization problem, we only allow for
five different infection probabilities: 1) for contacts in schools 2) for contacts in
preschools and nurseries. 3) for work contacts. 4) for households. 5) for other
contacts.

@@

In order to get a feeling for the infectiousness of each contact type it
is more intuitive to look at how many infections were actually caused by each contact
type. This is depicted in Figure~\ref{fig:infection_heatmap}. We can see that work and
other contacts are the main drivers of the pandemic, followed by infections in
households. Schools and preschools contribute fewer infections which is to be expected
given that there are much fewer students than working adults in the German population.
Nevertheless, Figure~\ref{fig:school_scenarios_detailed} shows that schools do have a
notable effect on the infection dynamic in the long run.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/infection_channels.png}
    \caption{Daily share of infections by contact type}
    \floatfoot{\noindent \textit{Note:} Daily share of infections that were contributed
    by each contact type. Darker colors mean that a larger share of infections were
    contributed by that contact type. The majority of infections take place in the
    workplace, in households and via other contacts. Schools and preschools contribute
    less infections, especially after hygiene measures have been introduced.}
    \label{fig:infection_heatmap}
\end{figure}

@@

Moreover, we estimate nine different multipliers that reflect how strongly other contacts
are reduced over time. The dates at which we switch between the multipliers usually
coincide with policy changes and is not determined from the \replaced[id=K]{case
numbers}{data}. The only exception to this are slight adjustments to parameters to
incorporate lockdown fatigue (towards the end of a lockdown period) or precautionary
contact reductions (in times of high incidences right before a lockdown is enacted). The
estimated other multipliers are also depicted in Figure~\ref{fig:other_multiplier}.

### 2021-07-14 src/paper/model/initial_conditions.tex
Finish going over appendix B. More type corrections, suggestions and comments.

Consider a situation where you want to start a simulation with the beginning set amidst
the pandemic. It means that several thousands of individuals should already have
recovered from the disease, be infectious, symptomatic or in intensive care at the start
of your simulation. Additionally, the sample of infectious people who will determine the
course of the pandemic in the following periods is likely not representative of the
whole population because of differences in behavior (number of contacts,
assortativity), past policies (school closures), etc.. The distribution of courses of
diseases in the population at the begin of the simulation is called initial conditions.

To come up with realistic initial conditions, we match reported infections from official
data to simulated individuals by available characteristics like age and geographic
information. The matching must be done for each day of a longer time frame like a month
to have individuals with possible health states. Then, health statuses evolve until the
begin of the simulation period without simulating infections by contacts. We also
correct reported infections for a reporting lag and scale them up to arrive at the true
number of infections.

>>>>

Consider a situation where you want to start a simulation with the beginning set amidst
the pandemic. It means that several thousands of individuals should already have
recovered from the disease, be infectious, symptomatic or in intensive care at the start
of your simulation. Additionally, the sample of infectious people who will determine the
course of the pandemic in the following periods is likely not representative of the whole
population because of differences in behavior (number of contacts, assortativity), past
policies (school closures), etc.. The distribution of \replaced[id=K]{health
states}{courses of diseases} in the population at the beginning of the simulation is
called initial conditions.

To come up with realistic initial conditions, we match reported infections from official
data to simulated individuals by available characteristics like age and geographic
information. The matching must be done for each day of a longer time frame like a month
to have individuals with all possible health states. Then, health statuses evolve until
the beginning of the simulation period without simulating infections by contacts. We also
correct reported infections for a reporting lag and scale them up \replaced[id=K]{by the
share of detected cases}{} to arrive at the true number of infections.

### 2021-07-14 src/paper/model/seasonality.tex
Join single plots and make single plots smaller plus various small improvements.
Fix typos, make suggestions and add comments to sections B.1 to B.7.
Finish going over appendix B. More type corrections, suggestions and comments.

\subsection{Seasonality}\comment[id=K]{Philipp suggests to write that we choose upper
bounds}
\label{subsec:seasonality}

@@

We follow \cite{Kuehn2020} and \cite{Gavenciak2021} in modeling seasonality in the
transmission of SARS-CoV-2 as a multiplicative factor on infection probabilities. The
factor follows a sine curve that reaches its maximum at January first and its minimum
on June 30.

@@

Where $\kappa_k$ is difference in the seasonality factor between peak infectiousness
and lowest infectiousness.

The subscript $k$ is needed because the strength of the seasonality effect differs
across contact types: Work, household and school contacts are likely to take place
inside even in summer. Thus they are only subject to seasonality due to factors that
influence the immune system. Other contacts (for example meeting friends and while doing
leisure activities) are mostly happening outside in the summer. Therefore, transmission
via those contacts should have a stronger seasonal pattern.

@@

The two seasonality curves are shown in Figure~\ref{fig:seasonality}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/data/seasonality}
    \caption{Seasonality by Type of Contact}
    \label{fig:seasonality}
    \floatfoot{\noindent \textit{Note:} We model seasonality as a factor that reduces the
    probability of infection of all encounters. The factor depends on the day and is
    calculated from a sinus shaped function with its maximum on January 1st. Since
    seasonality can affect the transmission both through physical conditions such as
    temperature and humidity as well as through the numbers of contacts that take place
    outside we assume two seasonality factors. One for other contacts which we expect to
    be strongly affected by fairer weather with a maximum reduction of 42\% in the
    infection probability. The other seasonality only makes contacts up to 21\% less
    infectious and is applied to household, work and school contacts.}
\end{figure}

>>>>

\subsection{Seasonality}
\label{subsec:seasonality}

@@

We follow \cite{Kuehn2020} and \cite{Gavenciak2021} in modeling seasonality in the
transmission of SARS-CoV-2 as a multiplicative factor on infection probabilities. The
factor follows a sine curve that reaches its maximum at January 1 and its minimum
on June 30.

@@

Where $\kappa_c$ is difference in the seasonality factor between peak infectiousness
and lowest infectiousness.

The subscript $c$ is needed because the strength of the seasonality effect differs
across contact types: Work, household and school contacts are likely to take place
inside even in summer. Thus they are only subject to seasonality due to factors that
influence the immune system. Other contacts (for example meeting friends and while doing
leisure activities) are mostly happening outside in the summer. Therefore, transmission
via those contacts should have a stronger seasonal pattern.

@@

The two seasonality curves are shown in Figure~\ref{fig:seasonality}.

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/results/figures/data/seasonality}
    \caption{Seasonality by Type of Contact}
    \label{fig:seasonality}
    \floatfoot{\noindent \textit{Note:} We model seasonality as a factor that reduces the
    probability of infection of all encounters. The factor depends on the day and is
    calculated from a sinus shaped function with its maximum on January 1. Since
    seasonality can affect the transmission both through physical conditions such as
    temperature and humidity as well as through the numbers of contacts that take place
    outside we assume two seasonality factors. One for other contacts which we expect to
    be strongly affected by fairer weather with a maximum reduction of 42\% in the
    infection probability. The other seasonality only makes contacts up to 21\% less
    infectious and is applied to household, work and school contacts.}
\end{figure}
